better title eventually

### 2015-05-11 cs261n-paper/paper.tex
Start of introduction.

\section{Introduction} %%% 
\indent \indent Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

>>>>

\section{Introduction} %%% 
% \indent \indent Talk about the results and contributions concretely.
% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
% Talk about the changes resulted in the Tor browser here.
% As short as possible summary of lessons learned, 
% and also a short as possible motivation for censorship work here. %yep, same.
% Talk about the experiment design quickly here.

We aim to improve user security by evaluating
and improving the usability of security software.
Both ``usability'' and ``security'' encompass many topics;
therefore we limit our scope and focus on
an important and timely use case:
user configuration of software to evade Internet censorship.
In this report, we detail the design of a usability-focused user experiment,
which we hope will be a benchmark for such studies
and guide their development in the future.

We hold that usability must be regarded as a security property.
It should be part of the design of security software.
Usable software not only decreases the risk of making mistakes
with dangerous security consequences,
but also provides a bridge over which users can
transition from substitutes that are less safe.
